---
title: 'CATLR Assessment Hacks'
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---
  
```{r setup,include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo=FALSE)
library(dplyr)
library(kableExtra)
```
  
***
  
## Objectives  
  
1. Facilitate an exchange of assessment ideas within a group of educators.  
2. Provide a low-stakes, safe space for educators to give and receive feedback on assessments for their courses.  
3. Initiate long-term connections between educators across different disciplines.  
  
***
  
## How It Works  
  
We'll have 5 meetings throughout the semester focused on specific types of assessment (see our [schedule](#schedule) below). Participants will exchange ideas and feedback on examples provided by CATLR as well as current work that participants bring in.   
  
Participants are encouraged to bring a relevant assessment to "workshop" during the session. This can be in any form or stage of completion, from a 1-sentence idea of something you would like to implement in class, to a fully-drafted, student-facing document.   
  
### Time Commitment  
  
In this "mix-and-match" series, participants can select the meetings they would like to attend. Although it is not required, participants are *strongly encouraged* to attend multiple meetings as applicable to them. If attending more than one session, attendees should register separately for both sessions via Eventbrite.   
  
***  

## Schedule {#schedule}  
  
```{r, echo=FALSE, eval=TRUE}
schedule <- as_tibble(read.csv("files/schedule.csv",stringsAsFactors = FALSE))
kable(schedule) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
  
***  
  
## Assessment Resources  
   
CATLR offers multiple programs and resources related to developing assessments for your courses.  
   
### Events  
  
* Spring 2021 events here! TBA  
  
### NEU Resources  
     
* [Assessment at CATLR](https://learning.northeastern.edu/explore/assessment/)  
* [Northeastern Information Technology Resources on Online Exams](https://service.northeastern.edu/tech?id=kb_article&sys_id=42ffbee8db7f5010540e4b80ba9619fe&utm_source=091120_facstaff&utm_medium=email&utm_campaign=tech_update)  
  
### Teaching Tips  
  
* [Transparent Assignment Design](https://learning.northeastern.edu/transparent-assignment-design/)  
* [Using Assessments to Enhance Learning](https://learning.northeastern.edu/using-assessments-to-enhance-learning/)  
* [Early/Midterm Course Feedback](https://learning.northeastern.edu/midterm-course-feedback/)  
* [Developing Rubrics](https://learning.northeastern.edu/developing-rubrics/)  
  

